### 2014-05-09 learn_experimental.tex
Edited thru 4.3

\section{Experimental Setup}

\label{s:experiment}
We describe our experimental procedure below.  First, we specify a set
of \textit{training scenarios}: a set of network configurations
(\S\ref{ss:nwkcfg}) that express the designer's imperfect model of the
network. Next, we specify an \textit{objective function}
(\S\ref{ss:objective}). The protocol-design process synthesizes a
congestion-control protocol that maximizes the value of this function,
averaged over the set of training scenarios. Finally
(\S\ref{ss:eval}), we specify a \textit{testing scenario} of network
configurations, which may be similar or dissimilar to the training
scenarios.

@@

@@

\subsection{Evaluation procedure}
\label{ss:eval}
To measure the difficulty of learning a congestion-control protocol
with an imperfect model of the eventual network, we choose a testing
scenario of network configurations and evaluate the Tao protocol on
it. All evaluations are performed in the ns-2
simulator. Using a different simulator for training and
testing helps give confidence that the congestion-control protocols
learned are robust to quirks in a simulator implementation.

We compare the performance of Tao protocols optimized for ``accurate''
models of the network against Tao protocols optimized for various
kinds of imperfect models, in order to measure how faithfully protocol
designers need to understand the network they are designing for. We
give the training and testing scenarios in a table.

For reference, we also compare the Tao protocols with two common schemes in wide use today:

>>>>

\section{Experimental setup}

\label{s:experiment}
We describe our experimental procedure below.  First, we specify a set
of \textit{training scenarios}: a set of network configurations
(\S\ref{ss:nwkcfg}) that express the designer's imperfect model of the
network. Next, we specify an \textit{objective function}
(\S\ref{ss:objective}). Remy synthesizes a congestion-control protocol
that attempts to maximize the value of this function, averaged over
the set of training scenarios. Finally (\S\ref{ss:eval}), we specify a
\textit{testing scenario} of network configurations, which may be
similar or dissimilar to the training scenarios.

@@

\begin{comment}

@@

\end{comment}

\subsection{Evaluation procedure}
\label{ss:eval}
To measure the difficulty of learning a congestion-control protocol
with an imperfect model of the eventual network, we choose a testing
scenario of network configurations and evaluate the RemyCC on it. All
evaluations are performed in the ns-2 simulator.\footnote{Using one
  simulator for training (Remy's internal simulator) and a different
  one for evaluation helps give confidence that the congestion-control
  protocols learned are robust to quirks in a simulator
  implementation.}

We compare the performance of RemyCCs optimized for an ``accurate''
model of the network against RemyCCs optimized for various
kinds of imperfect models, in order to measure how faithfully protocol
designers need to understand the network they are designing for. We
give the training and testing scenarios in a table.

For reference, we also compare the RemyCCs with two common schemes in wide use today:

### 2014-05-09 learn_learnability.tex
Edited thru 4.3

\section{Related Work}
\label{s: learnability}

@@

Formally speaking, designing such a protocol is a problem in
sequential decision-making under uncertain and can be modeled as a
Partially-Observable Markov Decision Process~\cite{pomdp}. In that
context, the purpose of this paper is to ask: how well can a protocol
designer ``learn'' the solution to one POMDP or set of networks and
successfully apply the result (a protocol) to a different set of networks?

>>>>

\section{Protocol design as a problem of learnability}
\label{s: learnability}

\begin{comment}

@@

\begin{comment}
Formally speaking, designing such a protocol is a problem in
sequential decision-making under uncertain and can be modeled as a
Partially-Observable Markov Decision Process~\cite{pomdp}. In that
context, the purpose of this paper is to ask: how well can a protocol
designer ``learn'' the solution to one POMDP or set of networks and
successfully apply the result (a protocol) to a different set of networks?
\end{comment}

### 2014-05-09 learn_operational.tex
Edited thru 4.3

Figure~\ref{f:multihop} shows the end-to-end throughput of connections
traversing two bottleneck links for different protocols, including two
RemyCCs. In each experiment, there were three flows: one that
traversed two hops (the measured connection), a cross-traffic flow
that traversed only the first bottleneck, and another cross-traffic
flow that traversed only the second bottleneck.

>>>>

%Figure~\ref{f:multihop} shows the end-to-end throughput of connections
%traversing two bottleneck links for different protocols, including two
%RemyCCs. In each experiment, there were three flows: one that
%traversed two hops (the measured connection), a cross-traffic flow
%that traversed only the first bottleneck, and another cross-traffic
%flow that traversed only the second bottleneck.
